\textbf{Analyzing Machupo virus-receptor binding by molecular dynamics simulations}

### 2014-01-05 paper.tex
Added two figures.

Despite, the fact that viral binding occurs at the site of a flexible loop in the free hTfR structure, our data shows after binding the strand is extremely rigid. None of the sites in the interfacial strand have root mean squared fluctuation (RMSF) values in the top half of all sites in the complex during equilibration (figure). This is unsurprising considering the high degree of burial that occurs as a result of viral binding. In addition, computing the root mean squared deviation (RMSD) of the entire structure over the trajectory shows that none of the mutations are so deleterious as the cause rapid unbinding. In fact, the RMSD over trajectory looks incredibly invariant across mutants (figure).

@@

>>>>

Despite, the fact that viral binding occurs at the site of a flexible loop in the free hTfR structure, our data shows after binding the strand is extremely rigid. None of the sites in the interfacial strand have root mean squared fluctuation (RMSF) values in the top half of all sites in the complex during equilibration (Figure~\ref{fig:rmsf}). This is unsurprising considering the high degree of burial that occurs as a result of viral binding. In addition, computing the root mean squared deviation (RMSD) of the entire structure over the trajectory shows that none of the mutations are so deleterious as the cause rapid unbinding. In fact, the RMSD over trajectory looks incredibly invariant across mutants (Figure~\ref{fig:rmsd}).

@@

\clearpage
\begin{figure}[p]
\centerline{\includegraphics[width=6in]{figures/rmsfs.pdf}}
\caption{\label{fig:rmsf}\title{RMSF values.} The RMSF values for every site in the bound complex computed during the equilibration phase of the protocol. Each color represents the average over 20 trajectories of a single mutant. The plot shows the flexibility of each site is essentially independent of mutation, and none of the sites above 0.72~\AA\ are found in the interface.}
\end{figure}

\clearpage
\begin{figure}[p]
\centerline{\includegraphics[width=6in]{figures/rmsds.pdf}}
\caption{\label{fig:rmsd}\title{RMSD values.} The RMSD values over the time of the trajectory computed during the equilibration phase of the protocol. Each color represents the average over 20 trajectories of a single mutant. The plot shows none of the mutants causes immediate unbinding of the protein--protein complex. In addition, the universal upward trend near the end of the equilibration trajectories may indicate the crystal is more tightly packed than would normally occur in solution.}
\end{figure}
